On Optimality of Finite Element Integration

### 2015-12-15 TOMS_Paper/assembly.tex
minor fixes

\begin{Algo}[Sharing elimination]
\label{algo:sharing-elimination}
\normalfont
The algorithm has three main steps: initialization (step 1); scheduling of multilinear operands, to reach quasi-optimality (steps 2-4); scheduling of all other sub-expressions (step 5).
\begin{enumerate}
\item Perform a depth-first visit of the expression tree with recursive collection of identical sub-expressions. For example, an expression $(a + a + b + c + a)$ would be transformed into $(3a + b + c)$.
\item Perform a depth-first visit of the expression tree to collect and partition multilinear operands into $p$ disjoint sets, $\mathbb{P} = \lbrace P^0, P^1, ..., P^{p-1}\rbrace$. $\mathbb{P}$ is such that multilinear operands in $P$ share a set of multilinear symbols, whereas there is no sharing across different partitions. Let $S_P$ be the set of multilinear symbols shared in $P$.
\item Calculate the cost of each $P \in \mathbb{P}$, as $c_P = {min(}|P|,\ |S_P|{)}$. Intuitively, $c_P$ indicates the number of operations induced by $P$ at every innermost loop iteration once sharing elimination will be applied. Take $P$ such that $c_P$ is minimum.
\item Choose the optimal strategy between points (i) and (ii), described in Section~\ref{sec:se-rln}. If $|P| < |S_P|$, (i) is applied. If $|P| > |S_P|$, (ii) is applied. Otherwise, $|P| = |S_P|$ means that (i) and (ii) have the same impact on the innermost loop. However, the increase in operation count in the outer loops, $i_l$, may still be different. In particular, if (i) were applied, $i_l = \sum_{o \in P} (c_{o}^{l} + n_{o} - 1)$, while if (ii) were applied, $i_l = \sum_{s \in S_P} (n_{s} - 1)$. Note that $n_o$ and $n_s$ capture the number of additions required after collection of $o$ and $s$. We then select (i) or (ii) such that $i_l$ is minimum. 
\item If $\mathbb{P} \setminus \lbrace P\rbrace$ is not empty, go back to point 2. Otherwise, step to point 6.
\item Perform a depth-first visit of the expression tree and, for each $L_i$-dependent expression, apply sharing elimination assuming a structured tensor operation is in place (i.e., as in point 4 above). The result may be sub-optimal if this speculative assumption does not hold (i.e., only a subset of code motion opportunities are exposed).
\end{enumerate}
\end{Algo}

>>>>

\begin{Algo}[Sharing elimination]
\label{algo:sharing-elimination}
\normalfont
The algorithm has three main steps: initialization (step 1); scheduling of multilinear operands, to reach quasi-optimality (steps 2-5); scheduling of all other sub-expressions (step 6).
\begin{enumerate}
\item Perform a depth-first visit of the expression tree with recursive collection of identical sub-expressions. For example, an expression $(a + a + b + c + a)$ would be transformed into $(3a + b + c)$.
\item Perform a depth-first visit of the expression tree to collect and partition multilinear operands into $p$ disjoint sets, $\mathbb{P} = \lbrace P^0, P^1, ..., P^{p-1}\rbrace$. $\mathbb{P}$ is such that multilinear operands in $P$ share a set of multilinear symbols $S_P$, whereas there is no sharing across different partitions.
\item Calculate the cost of each $P \in \mathbb{P}$, as $c_P = {min(}|P|,\ |S_P|{)}$. Intuitively, $c_P$ indicates the number of operations induced by $P$ at every innermost loop iteration once sharing elimination will be applied. Take $P$ such that $c_P$ is minimum.
\item Choose the optimal strategy between points (i) and (ii), described in Section~\ref{sec:se-rln}. If $|P| < |S_P|$, (i) is applied. If $|P| > |S_P|$, (ii) is applied. Otherwise, $|P| = |S_P|$ means that (i) and (ii) have the same impact on the innermost loop. However, the increase in operation count in the outer loops, $i_l$, may still be different. In particular, if (i) were applied, $i_l = \sum_{o \in P} (c_{o}^{l} + n_{o} - 1)$, while if (ii) were applied, $i_l = \sum_{s \in S_P} (n_{s} - 1)$. Note that $n_o$ and $n_s$ capture the number of additions required after factorization of $o$ and $s$. We then select (i) or (ii) such that $i_l$ is minimum. 
\item If $\mathbb{P} \setminus \lbrace P\rbrace$ is not empty, go back to point 2. Otherwise, step to point 6.
\item Perform a depth-first visit of the expression tree and, for each $L_i$-dependent expression, apply sharing elimination assuming a structured tensor operation is in place (i.e., as in point 4 above). The result may be sub-optimal if this speculative assumption does not hold (i.e., only a subset of code motion opportunities are exposed).
\end{enumerate}
\end{Algo}
